Proof of concept

### 2022-12-20 docs/src/paper/experiments/_mitigation_strategies.qmd
helper function for bootstrap with caching and multi-threading

## Mitigation Strategies

```{julia}
#| eval: true
using Pkg; Pkg.activate("dev")
```

```{julia}
#| eval: true
include("dev/utils.jl")
using AlgorithmicRecourseDynamics
using CounterfactualExplanations, Flux, Plots, PlotThemes, Random, LaplaceRedux, LinearAlgebra, Images
theme(:wong)
output_path = output_dir("mitigation_strategies")
www_path = www_dir("mitigation_strategies");
```

@@

### Synthetic

@@

```{julia}
n_evals = 5
n_rounds = 50
evaluate_every = Int(round(n_rounds/n_evals))
n_folds = 5
n_bootstrap = 1
T = 100
using Serialization
results = run_experiments(
    experiments;
    save_path=output_path,evaluate_every=evaluate_every,n_rounds=n_rounds, n_folds=n_folds, n_bootstrap=n_bootstrap, T=T
)
Serialization.serialize(joinpath(output_path,"results_synthetic.jls"),results)
```

### Plots

@@

#### Line Charts

@@

#### Error Bar Charts

@@

### Bootstrap

```{julia}
n_bootstrap = 1000
using AlgorithmicRecourseDynamics.Evaluation: evaluate_system
using DataFrames
df = DataFrame()
for (key, val) in results
    n_folds = length(val.experiment.recourse_systems)
    for fold in 1:n_folds
        for i in length(val.experiment.system_identifiers)
            rec_sys = val.experiment.recourse_systems[fold][i]
            model_name, gen_name = collect(val.experiment.system_identifiers)[i]
            df_ = evaluate_system(rec_sys, val.experiment; n=n_bootstrap)
            df_.model .= model_name
            df_.generator .= gen_name
            df_.fold .= fold
            df = vcat(df, df_)
        end
    end
end
df = mapcols(x -> typeof(x) == Vector{Symbol} ? string.(x) : x, df)
using RCall
save_path = joinpath(output_path, "bootstrap_synthetic.csv")
using CSV
CSV.write(save_path)
```

### Chart in paper

@@

### Latent Space Search

@@

```{julia}
n_evals = 5
n_rounds = 50
evaluate_every = Int(round(n_rounds/n_evals))
n_folds = 5
n_bootstrap = 1
T = 100
using Serialization
results = run_experiments(
    experiments;
    save_path=output_path,evaluate_every=evaluate_every,n_rounds=n_rounds, n_folds=n_folds, n_bootstrap=n_bootstrap, T=T
)
Serialization.serialize(joinpath(output_path,"results_synthetic_latent.jls"),results)
```

@@

### Plots

#### Line Charts

@@

### Bootstrap

```{julia}
n_bootstrap = 1000
using AlgorithmicRecourseDynamics.Evaluation: evaluate_system
using DataFrames
df = DataFrame()
for (key, val) in results
    n_folds = length(val.experiment.recourse_systems)
    for fold in 1:n_folds
        for i in length(val.experiment.system_identifiers)
            rec_sys = val.experiment.recourse_systems[fold][i]
            model_name, gen_name = collect(val.experiment.system_identifiers)[i]
            df_ = evaluate_system(rec_sys, val.experiment; n=n_bootstrap)
            df_.model .= model_name
            df_.generator .= gen_name
            df_.fold .= fold
            df = vcat(df, df_)
        end
    end
end
df = mapcols(x -> typeof(x) == Vector{Symbol} ? string.(x) : x, df)
using RCall
save_path = joinpath(output_path, "bootstrap_latent.csv")
using CSV
CSV.write(save_path)
```

### Chart in paper

@@

## Real World

```{julia}
generators = Dict(
    :Generic=>GenericGenerator(decision_threshold=0.5),
    :Latent=>REVISEGenerator(),
    :Generic_conservative=>GenericGenerator(decision_threshold=0.9),
    :Gravitational=>GravitationalGenerator(),
    :ClapROAR=>ClapROARGenerator()
)
```

```{julia}
max_obs = 2500
data_sets = AlgorithmicRecourseDynamics.Data.load_real_world(max_obs)
```

```{julia}
using CounterfactualExplanations.DataPreprocessing: unpack
bs = 50
function data_loader(data::CounterfactualData)
    X, y = unpack(data)
    data = Flux.DataLoader((X,y),batchsize=bs)
    return data
end
model_params = (batch_norm=false,n_hidden=32,n_layers=3,dropout=true,p_dropout=0.25)
```

```{julia}
experiments = set_up_experiments(
    data_sets,models,generators; 
    pre_train_models=100, model_params=model_params, 
    data_loader=data_loader
)
```

```{julia}
n_evals = 5
n_rounds = 50
evaluate_every = Int(round(n_rounds/n_evals))
n_folds = 5
n_bootstrap = 1
n_samples = 10000
T = 250
using Serialization
results = run_experiments(
    experiments;
    save_path=output_path,
    evaluate_every=evaluate_every,
    n_rounds=n_rounds, 
    n_folds=n_folds, 
    n_bootstrap=n_bootstrap, 
    T=T
)
Serialization.serialize(joinpath(output_path,"results_real_world.jls"),results)
```

```{julia}
using Serialization
results = Serialization.deserialize(joinpath(output_path,"results_real_world.jls"))
```

### Bootstrap

```{julia}
n_bootstrap = 1000
using AlgorithmicRecourseDynamics.Evaluation: evaluate_system
using DataFrames
df = DataFrame()
for (key, val) in results
    n_folds = length(val.experiment.recourse_systems)
    for fold in 1:n_folds
        for i in length(val.experiment.system_identifiers)
            rec_sys = val.experiment.recourse_systems[fold][i]
            model_name, gen_name = collect(val.experiment.system_identifiers)[i]
            df_ = evaluate_system(rec_sys, val.experiment; n=n_bootstrap)
            df_.model .= model_name
            df_.generator .= gen_name
            df_.fold .= fold
            df = vcat(df, df_)
        end
    end
end
df = mapcols(x -> typeof(x) == Vector{Symbol} ? string.(x) : x, df)
using RCall
save_path = joinpath(output_path, "bootstrap_real_world.csv")
using CSV
CSV.write(save_path)
```

### Chart in paper

>>>>

### Mitigation Strategies

```{julia}
#| echo: false

include("docs/src/paper/setup.jl")
eval(setup)
output_path = output_dir("mitigation_strategies")
www_path = www_dir("mitigation_strategies")
```

@@

#### Synthetic

@@

```{julia}
n_evals = 5
n_rounds = 50
evaluate_every = Int(round(n_rounds/n_evals))
n_folds = 5
T = 100
using Serialization
results = run_experiments(
    experiments;
    save_path=output_path,evaluate_every=evaluate_every,n_rounds=n_rounds, n_folds=n_folds, T=T
)
Serialization.serialize(joinpath(output_path,"results_synthetic.jls"),results)
```

#### Plots

@@

##### Line Charts

@@

##### Error Bar Charts

@@

#### Bootstrap

```{julia}
n_bootstrap = 1000
df = run_bootstrap(results, n_bootstrap; filename=joinpath(output_path,"bootstrap_synthetic.csv"))
```

#### Chart in paper

@@

#### Latent Space Search

@@

```{julia}
n_evals = 5
n_rounds = 50
evaluate_every = Int(round(n_rounds/n_evals))
n_folds = 5
T = 100
using Serialization
results = run_experiments(
    experiments;
    save_path=output_path,evaluate_every=evaluate_every,n_rounds=n_rounds, n_folds=n_folds, T=T
)
Serialization.serialize(joinpath(output_path,"results_synthetic_latent.jls"),results)
```

@@

#### Plots

##### Line Charts

@@

#### Bootstrap

```{julia}
n_bootstrap = 1000
df = run_bootstrap(results, n_bootstrap; filename=joinpath(output_path,"bootstrap_latent.csv"))
```

#### Chart in paper

@@

#### Bootstrap

```{julia}
n_bootstrap = 1000
df = run_bootstrap(results, n_bootstrap; filename=joinpath(output_path,"bootstrap_real_world.csv"))
```

#### Chart in paper

### 2022-12-20 docs/src/paper/experiments/_real_world.qmd
helper function for bootstrap with caching and multi-threading

## Real-World Data

```{julia}
#| eval: true
using Pkg; Pkg.activate("dev")
```

```{julia}
#| eval: true
include("dev/utils.jl")
using AlgorithmicRecourseDynamics
using CounterfactualExplanations, Flux, Plots, PlotThemes, Random, LaplaceRedux, LinearAlgebra
theme(:wong)
output_path = output_dir("real_world")
www_path = www_dir("real_world");
```

@@

### Experiment

```{julia}
n_evals = 5
n_rounds = 50
evaluate_every = Int(round(n_rounds/n_evals))
n_folds = 5
n_bootstrap = 1
n_samples = 10000
T = 250
generative_model_params = (epochs=250, latent_dim=8)
using Serialization
results = run_experiments(
    experiments;
    save_path=output_path,evaluate_every=evaluate_every,n_rounds=n_rounds, n_folds=n_folds, n_bootstrap=n_bootstrap, T=T, n_samples=n_samples,
    generative_model_params=generative_model_params
)
Serialization.serialize(joinpath(output_path,"results.jls"),results)
```

### Plots

@@

### Bootstrap

```{julia}
n_bootstrap = 1000
using AlgorithmicRecourseDynamics.Evaluation: evaluate_system
using DataFrames
df = DataFrame()
for (key, val) in results
    n_folds = length(val.experiment.recourse_systems)
    for fold in 1:n_folds
        for i in length(val.experiment.system_identifiers)
            rec_sys = val.experiment.recourse_systems[fold][i]
            model_name, gen_name = collect(val.experiment.system_identifiers)[i]
            df_ = evaluate_system(rec_sys, val.experiment; n=n_bootstrap)
            df_.model .= model_name
            df_.generator .= gen_name
            df_.fold .= fold
            df = vcat(df, df_)
        end
    end
end
df = mapcols(x -> typeof(x) == Vector{Symbol} ? string.(x) : x, df)
using RCall
save_path = joinpath(output_path, "bootstrap.csv")
using CSV
CSV.write(save_path)
```

### Chart in paper

>>>>

### Real-World Data

```{julia}
#| echo: false

include("docs/src/paper/setup.jl")
eval(setup)
output_path = output_dir("real_world")
www_path = www_dir("real_world");
```

@@

#### Experiment

```{julia}
n_evals = 5
n_rounds = 50
evaluate_every = Int(round(n_rounds/n_evals))
n_folds = 5
n_samples = 10000
T = 250
generative_model_params = (epochs=250, latent_dim=8)
using Serialization
results = run_experiments(
    experiments;
    save_path=output_path,evaluate_every=evaluate_every,n_rounds=n_rounds, n_folds=n_folds, T=T, n_samples=n_samples,
    generative_model_params=generative_model_params
)
Serialization.serialize(joinpath(output_path,"results.jls"),results)
```

#### Plots

@@

#### Bootstrap

```{julia}
n_bootstrap = 1000
df = run_bootstrap(results, n_bootstrap; filename=joinpath(output_path,"bootstrap.csv"))
```

#### Chart in paper

### 2022-12-20 docs/src/paper/experiments/_synthetic.qmd
helper function for bootstrap with caching and multi-threading

## Synthetic Data {#sec-app-synthetic}

@@

### Experiments

@@

include("docs/src/paper/setup.jl")
eval(setup)
```

@@

```{julia}
n_evals = 5
n_rounds = 50
evaluate_every = Int(round(n_rounds/n_evals))
n_folds = 5
n_bootstrap = 1
T = 100
results = run_experiments(
    experiments;
    save_path=output_path,evaluate_every=evaluate_every,n_rounds=n_rounds, n_folds=n_folds, n_bootstrap=n_bootstrap, T=T
)
Serialization.serialize(joinpath(output_path,"results.jls"),results)
```

@@

### Plots

```{julia}
#| eval: true
using Serialization
results = Serialization.deserialize(joinpath(output_path,"results.jls"));
```

@@

### Bootstrap

```{julia}
n_bootstrap = 1000
using AlgorithmicRecourseDynamics.Evaluation: evaluate_system
using DataFrames
df = DataFrame()
for (key, val) in results
    n_folds = length(val.experiment.recourse_systems)
    for fold in 1:n_folds
        for i in 1:length(val.experiment.system_identifiers)
            rec_sys = val.experiment.recourse_systems[fold][i]
            model_name, gen_name = collect(val.experiment.system_identifiers)[i]
            df_ = evaluate_system(rec_sys, val.experiment; n=n_bootstrap)
            df_.data .= key
            df_.model .= model_name
            df_.generator .= gen_name
            df_.fold .= fold
            df = vcat(df, df_)
        end
    end
end
df = mapcols(x -> typeof(x) == Vector{Symbol} ? string.(x) : x, df)
using RCall
save_path = joinpath(output_path, "bootstrap.csv")
using CSV
CSV.write(save_path, df)
```

### Chart in paper {#sec-app-synthetic-paper}

@@

using RCall
scale_ = 1.5
R"""
library(data.table)
df_plot <- data.table($df_plot)
name_order <- c(
    "MMD (domain)",
    "MMD (model)",
    "Performance",
    "Disagreement",
    "Decisiveness"
)
df_plot[,name:=factor(name, levels=name_order)]
model_order <- c("Linear", "MLP", "Deep Ensemble")
df_plot[,model:=factor(model, levels=model_order)]
library(ggplot2)
plt <- ggplot(df_plot) +
    geom_bar(aes(x=n, y=mean, fill=generator), stat="identity", alpha=0.5, position="dodge") +
    geom_pointrange(aes(x=n, y=mean, ymin=ymin, ymax=ymax, colour=generator), alpha=0.9, position=position_dodge(width=c(0.9,0.9)), size=0.5) +
    facet_grid(
        rows = vars(name),
        cols =  vars(model), 
        scales = "free_y"
    ) +
    labs(y = "Value") + 
    scale_fill_discrete(name="Generator:") +
    scale_colour_discrete(name="Generator:") +
    theme(
        axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        legend.position="bottom"
    )
temp_path <- file.path(tempdir(), "plot.png")
ggsave(temp_path, width=$ncol * $scale_,height=$nrow * $scale_ * 0.75) 
"""

>>>>

### Synthetic Data {#sec-app-synthetic}

@@

#### Experiments

@@

include("docs/src/paper/setup.jl")
eval(setup)
output_path = output_dir("synthetic") # output directory for artifacts
www_path = www_dir("synthetic")       # output directory for images
```

@@

```{julia}
n_evals = 5
n_rounds = 50
evaluate_every = Int(round(n_rounds/n_evals))
n_folds = 5
T = 100
results = run_experiments(
    experiments;
    save_path=output_path,evaluate_every=evaluate_every,n_rounds=n_rounds, n_folds=n_folds, T=T
)
Serialization.serialize(joinpath(output_path,"results.jls"),results)
```

@@

#### Plots

```{julia}
results = Serialization.deserialize(joinpath(output_path,"results.jls"));
```

@@

#### Bootstrap

```{julia}
n_bootstrap = 1000
df = run_bootstrap(results, n_bootstrap; filename=joinpath(output_path,"bootstrap.csv"))
```

#### Chart in paper {#sec-app-synthetic-paper}

@@

scale_ = 1.5
R"""
library(data.table)
df_plot <- data.table($df_plot)
name_order <- c(
    "MMD (domain)",
    "MMD (model)",
    "Performance",
    "Disagreement",
    "Decisiveness"
)
df_plot[,name:=factor(name, levels=name_order)]
model_order <- c("Linear", "MLP", "Deep Ensemble")
df_plot[,model:=factor(model, levels=model_order)]
library(ggplot2)
plt <- ggplot(df_plot) +
    geom_bar(aes(x=n, y=mean, fill=generator), stat="identity", alpha=0.5, position="dodge") +
    geom_pointrange(aes(x=n, y=mean, ymin=ymin, ymax=ymax, colour=generator), alpha=0.9, position=position_dodge(width=c(0.9,0.9)), size=0.5) +
    facet_grid(
        rows = vars(name),
        cols =  vars(model), 
        scales = "free_y"
    ) +
    labs(y = "Value") + 
    scale_fill_discrete(name="Generator:") +
    scale_colour_discrete(name="Generator:") +
    theme(
        axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        legend.position="bottom"
    )
temp_path <- file.path(tempdir(), "plot.png")
ggsave(temp_path, width=$ncol * $scale_,height=$nrow * $scale_ * 0.75) 
"""
